Data- and Systems Paper: Identifying Handicap Parking Spots for Event's Venues

### 2016-04-07 milestone1/paper/paper.tex
Added files via upload

\subsection{Theaters, Museums and Galleries Dataset}
The theaters and museums dataset contains the same features according to the JSON we used:

\begin{center}
	\textbf{\emph{Features}}
	\setlength{\columnsep}{6em}
\begin{multicols}{3}
	\begin{enumerate}
		\item \textbf{Trcid}
		\item \textbf{Title}
		\item \textbf{Shortdescription}
		\item \textbf{Longdescription}
		\item \textbf{Calendarsummary}
		\item \textbf{TitleEN}
		\item \textbf{ShortdescriptionEN }
		\item \textbf{LongdescriptionEN  }
		\item \textbf{CalendarsummaryEN       }
		\item \textbf{Types} 
		\item \textbf{Ids}
		\item \textbf{Locatienaam}
		\item \textbf{City}
		\item \textbf{Adres}
		\item \textbf{Zipcode}
		\item \textbf{Latitude}
		\item \textbf{Longitude}
		\item \textbf{Urls}
		\item \textbf{Media}
		\item \textbf{Thumbnail}
		\item \textbf{Datepattern\_startdate}
		\item \textbf{Datepattern\_enddate}
		\item \textbf{Singledates}
		\item \textbf{Type1}
		\item \textbf{Lastupdated}			
		\end{enumerate}
\end{multicols}
\end{center}

>>>>

\subsection{Theaters, Museums and Galleries Dataset}
The theaters and museums dataset contains the main features according to the JSON we used:

\begin{center}
	\textbf{\emph{Features}}
\begin{multicols}{2}
	\begin{enumerate}
		\item \textbf{Trcid}
		\item \textbf{Title}
		\item \textbf{Details *}
		\item \textbf{Types *}
		\item \textbf{Location *}
		\item \textbf{Urls *}
		\item \textbf{Media *}
		\item \textbf{Dates}
		\item \textbf{Lastupdated}
		\item \textbf{Eigenschappen *} 
		\end{enumerate}
\end{multicols}
\end{center}

The main features (*) in the JSON format that contain sub-features.
\renewcommand{\labelitemi}{$\bullet$}
\renewcommand{\labelitemii}{$\cdot$}
\renewcommand{\labelitemiii}{$\diamond$}
\renewcommand{\labelitemiv}{$\ast$}
\begin{multicols}{2}
	\begin{itemize}
		\item \textit{Details}\itemsep2pt
		\begin{itemize}\itemsep1pt
			\item language
			\item title
			\item calendarsummary
			\item shortdescription
			\item longdescription
		\end{itemize}
		\item \textit{Types}
		\begin{itemize}\itemsep1pt
			\item type
			\item catid
		\end{itemize}
		\item \textit{Location}
		\begin{itemize}
			\item name
			\item city
			\item address
			\item zipcode
			\item latitude
			\item longitude
		\end{itemize}
		\item \textit{Media}
		\begin{itemize}
			\item url
			\item main
		\end{itemize}
		\item \textit{Eigenschappen}
		\begin{itemize}
			\item Catid
			\item Value
			\item CategoryArea
			\item Category
		\end{itemize}
	\end{itemize}
\end{multicols}
